% !TeX program = pdflatex
% Kim Fernandes's Curriculum Vitae
% Email: kim_fernandes@brown.edu

% chktex-file 8
% chktex-file 13
% chktex-file 36

\RequirePackage[l2tabu,orthodox]{nag}
\documentclass[11pt,letterpaper]{report}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{ebgaramond}
\usepackage{tgheros}
\usepackage[USenglish]{babel}
\usepackage[strict,autostyle]{csquotes}
\usepackage[babel=true]{microtype}
\usepackage{datetime}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{tabto}
\usepackage{titlesec}
\usepackage{hyperref}

\newcommand{\myname}{Kim Fernandes}
\newcommand{\listtabwidth}{1.7cm}
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

\SetTracking{encoding=*, family=\sfdefault}{30}
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

\geometry{body={6.5in, 9.0in},left=1.0in,top=1.0in}
\setlength\parindent{0em}
\setstretch{0.9}
\newcommand{\listitemspace}{0.25em}
\renewenvironment{itemize}{\begin{list}{}{\setlength{\leftmargin}{0em}\setlength{\parskip}{0em}\setlength{\itemsep}{\listitemspace}\setlength{\parsep}{\listitemspace}}}{\end{list}}
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,labelindent=0em,topsep=0em,partopsep=0em,itemsep=\listitemspace,parsep=\listitemspace,font=\normalfont}
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}
\hypersetup{colorlinks=true,urlcolor=black,citecolor=black,linkcolor=black,pdfauthor={\myname},pdfkeywords={},pdftitle={\myname: Curriculum Vitae},pdfsubject={Curriculum Vitae},pdfpagemode=UseNone}

\begin{document}
    \raggedright{}
    \namefont{\myname}
    \vspace{1em}
    \begin{minipage}[t]{0.700\textwidth}
        Department of Anthropology \\
        Brown University
    \end{minipage}
    \begin{minipage}[t]{0.295\textwidth}
        \raggedleft{}
        \href{mailto:kim_fernandes@brown.edu}{kim\_fernandes@brown.edu}
    \end{minipage}

    \section*{Academic Appointments}
    \begin{itemize}
        \item Brown University Providence, RI\\
        Assistant Professor, Sociocultural Anthropology
        \item University of Toronto Toronto, ON\\
        Faculty of Information\\
        Postdoctoral Fellow, August 2024 - present
    \end{itemize}

    \section*{Education}
    \begin{itemize}
        \item University of Pennsylvania Philadelphia, PA\\
        School of Arts and Sciences, Graduate School of Education\\
        Joint Doctor of Philosophy in Anthropology and Education with distinction, Spring 2024\\
        Dissertation: Quantifying the Body: Disability, Data, and Governance in India\\
        Committee: Dr. Nikhil Anand (co-chair), Dr. Kathleen Hall (co-chair), Dr. Lisa Mitchell, Dr. Deborah Thomas, Dr. Vandana Chaudhry\\
        (Finalist for the Comparative and International Education Society’s Gail P. Kelly Award for Outstanding Doctoral Dissertation)\\
        Certificates: Social, Cognitive and Affective Neuroscience (received May 2019); Graduate Teaching and Learning\\
        Anthropology Comprehensive Exams: Cultural Anthropology (High Pass), Linguistic Anthropology (High Pass), Biological Anthropology (Pass)\\
        Master of Education in Statistics, Measurement, Assessment and Research Technologies\\
        May 2019
        \item Harvard University Cambridge, MA\\
        Graduate School of Education Cumulative GPA: 3.76\\
        Master of Education in International Education Policy, May 2014
        \item Georgetown University Doha, Qatar\\
        School of Foreign Service in Qatar Cumulative GPA: 3.85\\
        Bachelor of Science in Foreign Service, International Politics, magna cum laude, Phi Beta Kappa, May 2011\\
        Certificate in American Studies\\
        Honor Society Awards: Alpha Sigma Nu, Omicron Delta Epsilon, Phi Alpha Theta
    \end{itemize}

    \section*{Affiliations}
    \begin{itemize}
        \item Digital Inquiry, Speculation, Collaboration and Optimism Network, University of Michigan
        \item Data \& Society Research Institute
        \item Center for Information, Technology and Public Life
    \end{itemize}

    \section*{Publications}
    \subsection*{Journal Articles}
    \begin{itemize}
        \item Fernandes, Kim. 2024. “Challenging Ableism: A Critical Turn Toward Disability Justice in HCI.” Co-authored with Cella M. Sum, Franchesca Spektor, Rahaf Alharbi, Leya Breanna Baltaxe-Admony, Erika Devine, Hazel Anneke Dixon, Jared Duval, Tessa Eagle, Frank Elavsky, Leandro S. Guedes, Serena Hillman, Vaishnav Kameswaran, Lynn Kirabo, Tamanna Motahar, Kathryn E. Ringland, Anastasia Schaadhardt, Laura Scheepmaker, and Alicia Williamson. XRDS Crossroads. 30 (4): 50 – 55.\newline\href{https://doi.org/10.1145/3665602}{https://doi.org/10.1145/3665602}
        \item Fernandes, Kim. 2023. “For Graduate Students, When the Sadness is Unbelievable: How to Research and Write if We Must When the World is on Fire.” Article in “Crip Pandemic Life: A Tapestry,” special section of Lateral: Journal of the Cultural Studies Association. 12 (1).\newline\href{https://doi.org/10.25158/L12.1.13}{https://doi.org/10.25158/L12.1.13}
        \item Fernandes, Kim. 2022. “Inclusive Education in Practice: Disability, ‘Special Needs’, and the (Re)production of Normativity in Indian Childhoods.” Children’s Geographies.\newline\href{https://doi.org/10.1080/14733285.2022.2124845}{https://doi.org/10.1080/14733285.2022.2124845}
        \item Fernandes, Kimberly P. and Rabani Garg. 2020. “Anxiety and the Politics of Child Well-Being During COVID-19.” NEOS: A Publication of the Anthropology of Children and Youth Interest Group
    \end{itemize}
    \subsection*{Other Peer-Reviewed Writing}
    \begin{itemize}
        \item Fernandes, Kim. 2024. “Pedagogies for a Particular Time.” Society for Cultural Anthropology Teaching Tools. June 6.
        \item Fernandes, Kim. 2022. “The Body, Spread Out Into A Database.” In Parables of AI In/From the Majority World: An Anthology, edited by Rigoberto Lara Guzman, Ranjit Singh and Patrick Davison. Data \& Society. December 7.
        \item Fernandes, Kim. 2022. “Counting as Care: Disability in Ethnographic Praxis.” Society for Cultural Anthropology Fieldsights: Theorizing the Contemporary, Disability as Rupture. Edited by Michele Friedner and Matthew Wolf-Meyer. September 6.
    \end{itemize}
    \subsection*{Book Chapters}
    \begin{itemize}
        \item Fernandes, Kim. 2025. “Assembling the Field During a Crisis: Disabled Carework and/as Fieldwork.” The Disabled Anthropologist, edited by Sumi Colligan and Anna Jaysane-Darr. Routledge.
        \item Fernandes, Kim. 2024. “Madness and Resilience: Nethnographic Perspectives on Finding and Forming Community.” Mad Scholars Anthology, edited by Shayda Kafai and Melanie Jones. Syracuse University Press.
        \item Fernandes, Kimberly P. and Tanushree Sarkar. 2023. “Beyond Vulnerable/Tragedies: Educational Access for Disabled Children During COVID-19 in India.” Research in Social Science and Disability: Disability in the Time of the Pandemic, Volume 13. Edited by Allison C. Carey, Sara E. Green and Laura Mauldin. Emerald Publishing Ltd.\newline\href{https://doi.org/10.1108/S1479-354720230000013006}{https://doi.org/10.1108/S1479-354720230000013006}\\[0.5\baselineskip]
[Chapter received the Best Chapter Award \& Outstanding Author Contribution Award]
        \item Fernandes, Kimberly P. 2023. “(Dis)ability, Sports and Educational Selves Outside School: Extracurricular Activities for Disabled Children in India.” Childhood and Youth in India: Engagements with Modernity, edited by Divya Kannan and Anandini Dar. Palgrave Mcmillan.\newline\href{https://doi.org/10.1007/978-3-031-31820-7}{https://doi.org/10.1007/978-3-031-31820-7}
    \end{itemize}
    \subsection*{Book Reviews}
    \begin{itemize}
        \item Review of Lives of Data: Essays on Computational Cultures from India, edited by Sandeep Mertia. IEEE Annals of the History of Computing. April – June 2022.\newline\href{http://dx.doi.org/10.1109/MAHC.2022.3169868}{http://dx.doi.org/10.1109/MAHC.2022.3169868}
        \item Review of Disability and Colonialism: (Dis)encounters and Anxious Intersectionalities by Karen Soldatic and Shaun Grech (eds.). Disability Studies Quarterly. Spring 2021.\newline\href{http://dx.doi.org/10.18061/dsq.v41i1.7885}{http://dx.doi.org/10.18061/dsq.v41i1.7885}
        \item Review of Contemplating Dis/Ability in Schools and Society: A Life in Education by David J. Connor. Disability Studies Quarterly. Spring 2020.\newline\href{http://dx.doi.org/10.18061/dsq.v40i1.7424}{http://dx.doi.org/10.18061/dsq.v40i1.7424}
        \item Review of Sexual Citizens: A Landmark Study of Sex, Power and Assault on Campus, by Jennifer S. Hirsch and Shamus Khan. [forthcoming in 2024]. Anthropology and Education Quarterly.
    \end{itemize}
    \subsection*{In Preparation}
    \begin{itemize}
        \item Fernandes, Kim, Jiya Pandya, and Tanushree Sarkar. (Convenors and Editors) “Peripheral Crip Critique: Disability and Crip Theory in the Global South.” Special Issue for Disability Studies Quarterly.
        \item Fernandes, Kim, Kaiying Cindy Lin, and Kate Elliott. “A (S)low Carbon Ethnographic Invitation.” [Under revision for Low Carbon Research Methods: Making Equity and Epistemological Gains through Decarbonising Academic Work]
        \item Fernandes, Kim. “Fragmentary Citizenship: A Virtual Ethnography of Disability Identification in India.” [In preparation for submission to Engaging Science, Technology and Society]
    \end{itemize}

    \section*{Awards, Grants, Honors and Fellowships}
    \subsection*{External}
    \begin{itemize}
        \item Summer Writing Fellowship, Purdue University AARC (\$250) 2021
        \item Marion Jemmott Fellowship, Taraknath Das Foundation (\$7000) 2020
        \item Mellon International Dissertation Research Fellowship (SSRC, \$25,000) 2020
        \item American Institute of Indian Studies Junior Fellowship (alternate) 2020, 2021
    \end{itemize}
    \subsection*{Internal}
    \begin{itemize}
        \item Graduate Fellow, Andrea Mitchell Center (\$30,547 9-month stipend \& tuition) 2022 – 2023
        \item Sobti Family Doctoral Fellow, Center for the Advanced Study of India (\$12500) 2022 – 2023
        \item Graduate Associate, Perry World House 2022 - 2023
        \item Mellon Humanities, Urbanism and Design Graduate Research Award (\$2000) 2021
        \item Graduate and Professional Student Association Provost’s Fellowship (\$6000) 2021
        \item Center for the Advanced Study of India (CASI) summer funding (\$3500) 2021
        \item Morris S. Viteles Fellowship (\$25,800 9-month stipend and full tuition) 2016 – 2019
        \item Dean’s Summer Research Fellowship (\$5400 per summer) 2017 - 2019
        \item Harvard Graduate School of Education Scholarship (\$18,000) 2013 - 2014
        \item Georgetown University in Qatar Scholarship (\$15,000 per year) 2007 – 2011
    \end{itemize}

    \section*{Conference Participation}
    \begin{itemize}
        \item Society for Applied Anthropology (SfAA) 2021
        \item Society for the Social Studies of Science (4S) 2020
        \item NSF Society for the History of Technology (SHOT) 2020
    \end{itemize}

    \section*{Teaching \& Mentoring Experience}
    \subsection*{Instructor of Record}
    \begin{itemize}
        \item Education, Culture \& Society Graduate Seminar Fall 2023, Spring 2024
        \item SNF Paideia Proseminar Fall 2023
    \end{itemize}
    College Houses and Academic Services, University of Pennsylvania Philadelphia\\
    Graduate Associate August 2017- May 2019; August 2022 – May 2024
    \begin{itemize}
        \item Fostering a positive living environment designed to link community, faculty, and 32 residents, often resolving conflict, implementing and enforcing all University and Housing policies
        \item Developing and marketing student-centered hall programs to foster a house-wide community
        \item Budgeting and allocating use for an overall annual budget of \$6000 for floor and house events
    \end{itemize}
    Georgetown University School of Foreign Service in Qatar Doha, Qatar\\
    English Instructor June 2013, June 2018, July 2019, July 2022
    \begin{itemize}
        \item Teaching the processes of academic writing and critical thinking to prepare high school students for university-level work
        \item Developing learning materials tailored to student needs and course objectives, including opportunities for regular feedback
    \end{itemize}
    Mentor Me India Cambridge, MA\\
    Curriculum Lead October 2013 – May 2014
    \begin{itemize}
        \item Creating a curriculum for a year-long mentorship program between students in government schools and working professionals
        \item Coordinating conversations and seminars between experts on mentorship in the India and the US to understand specific needs of students in grades 6 – 8
    \end{itemize}
    Teach For India Mumbai, India\\
    5\textsuperscript{th} Grade Class Teacher, Municipal Corporation of Greater Mumbai June 2011 – May 2013
    \begin{itemize}
        \item Led 65 students to achieve 165\% academic growth in English and Math, thus moving them in English from a kindergarten level to a 2nd grade level in one year, and bringing them up to grade level in Math
        \item Initiated the school's first sustainable soccer training program by matching players from local and state level teams to train over 50 students and form teams for both boys and girls
    \end{itemize}

    \section*{Panels, Workshops and Roundtables Organized}
    \begin{itemize}
        \item Roundtable Co-Organizer (with Clara Beccaro). “Debility \& Violence: Attending to the State and Its Effects During an Extraordinary Time.” American Anthropological Association Annual Meeting, November 2024 (scheduled).
        \item Pre-Conference Symposium Co-Organizer (with Dr. Michele Friedner) \& Presenter. “South Asian Disability Futures.” Annual Conference on South Asia, October 2023.
        \item Roundtable Co-Organizer. “Writing and Researching Disability in India.” Annual Conference on South Asia, October 2023.
        \item Panel Co-Organizer \& Presenter. “Of the Body Politic, For the Body Politic: Counting Embodiment, Making Data.” Annual Conference on South Asia, October 2023.
        \item Session Co-Organizer \& Presenter. “Creating Crip Care Networks in Academia.” American Association of Geographers Annual Meeting, March 2023.
    \end{itemize}

    \section*{Selected Scholarly Participation}
    \begin{itemize}
        \item Roundtable Participant. “Technologies from the South as Method and Challenge.” American Anthropological Association Annual Meeting, November 2023.
        \item “Negotiating Ordinal Citizenship: Quantifying and Certifying Disability in India.” Imagined Bodies Conference, September 2023.
        \item “Counting As Care: Disability In/And/As Ethnographic Praxis.” American Association of Geographers Annual Meeting, March 2023.
        \item “Practices of Repair: Chronic Illness Methodologies for Studying the Politics of Numbers.” Mixed Realities Workshop, February 2023.
        \item “Re-Imagining Ethnography: Disability and Pandemic Rupture.” Society for the Social Studies of Science Annual Conference, December 2022.
        \item “Roundtable: Transforming Anthropological Landscapes Through Disability Anthropology.” American Anthropological Association Annual Meeting, November 2022.
        \item “Infrastructuring Exclusion: Disability, Certification and Citizenship in India.” Annual Conference on South Asia, University of Wisconsin-Madison, October 2022.
        \item “Knowing (From) the Body: Cripping Fieldwork During and After COVID-19.” Enacting Disability Justice, Critical Disability Studies Student Association, April 2021.
        \item “When Am I Really Successful? Disability, Design, and the Making of Inclusive Technologies.” Society for Disability Studies (virtual participant), April 2021.
        \item “Excessive Childhoods, Self-Reliant Citizens: Discursive Constructions of Care for Disabled Children in India During the COVID-19 Pandemic.” Association of Social Anthropologists (virtual participant), March 2021.
        \item “Making the Margins Through Identification and Enumeration: What Does It Take to Be Counted as Disabled in India?” Society for Applied Anthropology (virtual participant), March 2021.
        \item “Making the Disabled Body Legible: Biometrics, Documentary Evidence and the Indian State.” Society for Social Studies of Science, Prague (virtual participant), August 2020.
        \item “Negotiating Place, Establishing Identity: Disabled Children, Their Caregivers and the Formation of Educational Experiences.” Childhood, Youth and Identity in South Asia, New Delhi, January 2020.
        \item “Quantifying Disability, Generating Statistics: The Production of Inclusive Education in Urban India.” Comparative Education Society of India, Delhi, December 2019.
        \item “At the Margins, Between the Intersections: A History of Disability and Enumeration Under the Indian Census.” International Conference on Disability and Diversity in Asia, Malang, September 2019.
        \item “Ontologies of Difference in Data Collection: Disability and the Indian Census.” Society for Social Studies of Science, New Orleans, September 2019.
        \item “What Does It Mean To Be Disabled Enough In India?” Society for Disability Studies, Ohio, March 2019.
    \end{itemize}

    \section*{Invited Workshop Participation}
    \begin{itemize}
        \item Participant, “Shady Subjects.” Cornell University, 2025.
        \item Participant, “Revisiting Biomedicalization.” Yale University, 2025.
        \item Participant, “Mixed Realities: Ethnographic Approaches to the Virtual.” Yale University, 2023.
        \item Participant, “Algorithmic Reparation Workshop.” University of Michigan, 2022.
        \item Participant, “Dreaming Disability Justice in Human-Computer Interaction.” ACM CHI Conference on Human Factors in Computing Systems, 2022.
        \item Participant, Association of Internet Researchers, Doctoral Colloquium, 2021.
        \item Participant, “The Future of Care Work: Towards a Radical Politics of Care in CSCW Research and Practice.” 24th ACM Conference on Computer-Supported Cooperative Work and Social Computing, 2021.
        \item Participant, “Educational Transformations and Societal Change in Liberalizing India.” Spencer Foundation Workshop. Ahmedabad University, January 9 – 11 2020.
    \end{itemize}

    \section*{Other Invited Academic Training \& Participation}
    \begin{itemize}
        \item Participant, Digital IDEAS Summer Institute, 2021.
        \item Certificate Program Participant, Harvard STS Summer School, 2021.
        \item Participant, Low Carbon Research Methods Workshop, 2021.
        \item Participant, Disrupted Ethnography Autumn School, 2021.
        \item Participant, “Research, Interrupted,” ITU DK, 2020.
    \end{itemize}

    \section*{Media and Public Scholarship}
    \subsection*{Policy Reports}
    \begin{itemize}
        \item Digital Identity: Emerging Trends, Debates and Controversies. Co-authored with Dr. Eve Hayes deKalaf. Women in Identity. 2023.
    \end{itemize}
    \subsection*{Syllabi}
    \begin{itemize}
        \item A Primer on AI In/From the Majority World: An Empirical Site and a Standpoint. With Sareeta Amrute, Ranjit Singh, Rigoberto Lara Guzman, Aishatu Gwadabe, Dibyadyuti Roy, Murali Shanmugavelan, Nicolas Llano Linares, Paola Ricuarte Quijano, Soledad Magnone and Vasundhra Dahiya. 2022.
    \end{itemize}
    \subsection*{Public Scholarship}
    \begin{itemize}
        \item “The Statecraft of Digital IDs: An Annotated Bibliography.” With Ranjit Singh. Data and Society: Points. 2021.
        \item “Stitching Together the Patches for Ethnography,” Patchwork Ethnography: Conversations. 2021.
        \item “Choosing Otherwise: On Disabled Refusal.” Critical Childhood and Youth Studies Collective, August 2021.
        \item “Disability, Assistive Technologies and the ‘Special’ Needs of Children.” Critical Childhood and Youth Studies Collective, January 2021.
        \item “Sheena Kalayil Discusses Her Book, Second-Generation South Asian Britons,” CaMP Anthropology. 2021.
    \end{itemize}
    \subsection*{Podcasts}
    \begin{itemize}
        \item Graduate Co-Host, Criticism Inside, Alternatives Alongside: Organizing Otherwise to Intervene in Anthropology’s Future (Wenner-Gren Foundation for Anthropological Research)
        \item Co-Host, Platypod, Episodes 1 (Technologies and Politics of Accessibility) and 2 (Ableism in Anthropology and Higher Ed)
    \end{itemize}
    \subsection*{Other Creative Engagements}
    \begin{itemize}
        \item “The Immediacy of Broken Time: Sensing the Self During COVID-19 Fieldwork,” Feeling Digital Collective.
        \item Three Ways of Unpeeling Time When the Apocalypse Is Mundane and Excruciatingly Slow, with Sonaksha Iyengar, Riddhi Dastidar, Janani Vaidya, and Shazia Salam.
        \item Contributor, Pyaar Plus: Let’s Talk About Desire and Pleasure
        \item Contributor, \#TakeBackTheTech Mixtape
    \end{itemize}
    \subsection*{Other Invited Writing}
    \begin{itemize}
        \item Fernandes, Kim. 2023. “Finding Time and Stretching Space: Crip Friendships During the Pandemic.” In Yaari: An Anthology on Friendship by Women and Queer Folx. Edited by Shilpa Phadke and Nithila Kanagasabai. Yoda Press: New Delhi, India.
        \item Fernandes, Kim. 2022. “Cripping Queer Utopias: Making Room for Access, Care and Interdependence.” In Re(imagining) Queer Utopias: Voices from South Asia. Edited by Shahkawat Hossain Rajeeb. Shuddashar: Skien, Norway.
    \end{itemize}

    \section*{Selected Committee Service}
    \begin{itemize}
        \item Accessibility, Diversity \& Inclusion Chair, ACM COMPASS Conference on Computing and Sustainable Societies 2025
        \item LaborTech Annual Showcase Organizing Committee 2024
        \item Steering Committee, Harvard Graduate Research on STS Conference 2021
        \item Dean’s Committee on Race, Equity \& Inclusion, Graduate School of Education 2016 – 2019
        \item International Student Advisory Board, International Student \& Scholar Services 2017 – 2021
        \item RAGA Advisory Board, College Houses and Academic Services 2018 - 2019
        \item Doctoral Student Advisory Board, Graduate School of Education 2016 – 2018
        \item Committee on Open Expression, University of Pennsylvania 2016 – 2017
    \end{itemize}

    \section*{Editorial and Reviewing Activities}
    \begin{itemize}
        \item Managing Editor, Platypus – The CASTAC Blog 2025 - present
        \item Reviewer, CSCW Conference on Computer Supported Cooperative Work and Social Computing (2025)
        \item Reviewer, FAccT Conference on Fairness, Accountability and Transparency (2025)
        \item Reviewer, CHI Conference on Human Factors in Computing Systems (2025)
        \item Program Committee Member, ICTD Conference on Information \& Communication Technologies \& Development (2024)
        \item Tapuya: Latin American Science, Technology and Society 2024 – present
        \item Children’s Geographies
        \item Big Data \& Society 2023 – present
        \item Feminist Anthropology 2022 - present
        \item Contributing Editor, Platypus – The CASTAC Blog 2021 - 2024
        \item Disability Studies Quarterly 2020 - present
        \item NEOS | Anthropology of Children and Youth Interest Group 2020 - present
        \item Perspectives on Urban Education 2016 – present
        \item Journal of Critical Scholarship on Higher Education and Student Affairs 2019 - present
        \item Gulf Education and Social Policy Review 2019 – present
        \item Book Review Editor, African Policy Review Journal (Harvard Kennedy School) 2013 – 2014
    \end{itemize}

    \section*{Community Involvement}
    \begin{itemize}
        \item Volunteer, Disability Justice Network of Ontario 2024 - present
        \item Alumni Advisory Board Member, Teach for India 2019 - 2021
        \item Volunteer, National Platform for the Rights of the Disabled (India) 2020 – 2022
        \item Organizer, Alternative Justice India
    \end{itemize}

    \section*{Mentorship}
    \begin{itemize}
        \item Student Mentor, Society for Social Studies of Science Conference 2020 - 2022
        \item Wedu Rising Star 2020 – 2021
        \item Mentor, World Innovation Summit for Education 2020 - 2021
        \item Mentor, Graduate Student Mentoring Initiative 2018 - 2019
        \item Mentor, Graduate School of Education Mentor \& Mentee Program 2018 – 2019
        \item Mentor, LGBT Center Mentoring Program 2018 - 2019
        \item Alumni Ambassador, Harvard Graduate School of Education 2018 - 2023
    \end{itemize}

    \section*{Research Experience}
    \begin{itemize}
        \item Ministry of Rural Development, Government of India New Delhi, India\\
        Monitoring and Evaluation Specialist, DDU-GKY October 2015 – April 2016
        \item Tata Institute of Social Sciences Mumbai, India\\
        Visiting Scholar, National Corporate Social Responsibility Hub July 2015 – October 2015
        \item Abdul Latif Jameel Poverty Action Lab (J-PAL) Bhubaneswar, India\\
        Research Associate, Early Childhood Development July 2014 – June 2015
        \item Indus Action New Delhi, India\\
        Early Childhood Researcher July 2015 – July 2016, September 2012 – December 2013
    \end{itemize}

    \section*{Professional Memberships}
    \begin{itemize}
        \item American Anthropological Association
        \item Society for Applied Anthropology
        \item Society for Disability Studies
        \item Society for the Social Studies of Science
        \item Society for the History of Technology
    \end{itemize}

    \section*{Other Relevant Coursework}
    \begin{itemize}
        \item AI \& Algorithmic Auditor Certificate Program Spring 2023 - present
        \item South Asian Diploma in Narrative Practices 2022
        \item Storytelling Methodologies 2021
    \end{itemize}

    \section*{Quantitative Software Skills}
    \begin{itemize}
        \item Stata (proficient)
        \item R (comfortable)
        \item SAS (intermediate)
        \item SPSS (beginner)
        \item Python (beginner)
    \end{itemize}

    \section*{Languages}
    \begin{itemize}
        \item English (native)
        \item Hindi (fluent)
        \item Urdu (intermediate)
        \item Punjabi (beginner)
        \item Kannada (beginner)
    \end{itemize}

    \section*{References}
    \begin{tablist}
        \item[] Dr. Nikhil Anand\\
        Daniel Braun Silvers \& Robert Peter Silvers Family Presidential Professor of Anthropology\\
        Associate Faculty Director, Center for the Advanced Study of India, University of Pennsylvania\\
        \href{mailto:nikhil.anand@sas.upenn.edu}{nikhil.anand@sas.upenn.edu}
        \item[] Dr. Kathleen Hall\\
        Associate Professor of Education \& Anthropology, University of Pennsylvania\\
        \href{mailto:kdhall@upenn.edu}{kdhall@upenn.edu}
        \item[] Dr. Lisa Mitchell\\
        Professor of Anthropology \& History, University of Pennsylvania\\
        Chair, Department of South Asia Studies\\
        \href{mailto:lmitch@sas.upenn.edu}{lmitch@sas.upenn.edu}
    \end{tablist}

\end{document}
